Linear response theory for core set identification

### 2013-06-02 writedown/linear.response/paper.tex
add tex file for paper

\section{Perturbation from equilibrium state}
\subsection{The linear response theory}
In this sub-section, we give a brief description of the linear response

@@

example. Here we assume the system is governed by the
perturbed Langevin equation:

@@

  \dot{\vect q} & = \nabla_{\vect p}\mh(\vect q,\vect p)
  + \vect C(\vect q,\vect p) F_e(t)\\\label{eqn:langevin-2}

@@

  + \sigma\dot{\vect W}

@@

Where $\vect C$ and $\vect D$ are perturbations to the system, and
$F_e(t)$ is the strength of the perturbation as a function of time,
and is of order $\mo (\varepsilon)$, where $\varepsilon$ is assumed to be small.

@@

  \nabla_{\vect q}\cdot\vect C + \nabla_{\vect p}\cdot\vect D = 0

@@

The equilibrium and unperturbed system

@@

vanishing input perturbation $F_e(t) = 0$ in

@@

We assume that the perturbation to the

@@

distribution and the unperturbed operator
($\vect C = \vect D = 0$),

@@

which is the unperturbed equation. Matching the first and the second order gives:

@@

inital conditions $f_1(\vect x, 0) = 0$ and $f_2(\vect x, 0) = 0$

@@

Where $\bwg^\beta_0$ is the infiniesimal generator of the \emph{unperturbed} 

@@

where $\vect X^\beta_t$ is the trajectory of the unperturbed Langevin equation

@@

\subsection{The linear response theory for the core set identification}

The core set plays a very important role in the MSM theory. One way to
identify core set is to consider the ``stability'' of the invariant
measure $f^\beta_{\inv}$ under a propagator $\mt_\tau$
of time step $\tau$.
For example, the propagator is chosen $\mt_\tau = e^{\tau\fwg_t^{2\beta}}$,
i.e. integrating the Langevin equation~\eqref{eqn:langevin-1}
and \eqref{eqn:langevin-2} at temperature $1/2\beta$ for time $\tau$.
Notice $\tau$ is an artificial time that is ``orthogonal'' to the real
time $t$.
% , which is associated with a
% stochastic process denoted by $\vect Y_\alpha$:
The core set is identified by:

@@

  C_\tau(t) = \big\{
  \vect x \,\vert\, \mt_\tau f(\vect x, t) > f(\vect x, t)

@@

Generally, it is impossible and not necessary to consider the core set
in the $3N$ dimensional configuration space. For example, a
macromolecule solving in water, the DOFs of water is not of interest
at all. Therefore, we consider some phase space compressing function
$\vect y = \vect y(\vect x)$, with $\vect y \in \Omega \subset \mathbb
R^M,\ M\ll 3N$. We call $\Omega$ the observation space.  The projected
invariant measure on the observation space is therefore

@@

  \proj f (\vect y, t)

@@

  \int
  \dd \vect x\,
  f(\vect x, t) \,
  \delta (\vect y - \vect y(\vect x)) 

@@

The core set on the observation space is
  \widetilde
  C_\tau(t) = \big\{
  \vect y \,\vert\,
  \proj\mt_\tau f(\vect y, t) > \proj f(\vect y, t)
% with $\widetilde \mt_\alpha$ defined by
% $\widetilde\mt_\alpha = \mathcal P\circ\mt_\alpha$, namely
% \begin{align}
%   \widetilde\mt_\alpha\, p_0(\vect y)
%   =
%   \mathcal P\circ\mt_\alpha f_0 (\vect y)
%   =
%   \int
%   \dd \vect x\,
%   [\mt_\alpha f_0](\vect x) \,
%   \delta (\vect y - \vect y(\vect x)) 
% \end{align}
For convenience, we define $\Delta \mt_\tau =
\mt_\tau - \mathcal I$, where $\mathcal I$ is the
identity. If $[\proj\circ\Delta \mt_\tau f](\vect y, t) > 0$, then
$\vect y$ is in the core set $\widetilde C_\tau(t) $.
  [\proj\circ\Delta \mt_\tau f](\vect y, t)
  \int
  \dd \vect x\,
  \Delta \mt_\tau f(\vect x, t) \,
  \delta (\vect y - \vect y(\vect x))  \\\nonumber
  \lim_{\sigma \rightarrow 0}
  \int
  \dd \vect x\,
  \Delta \mt_\tau f(\vect x, t) \,
  K_{\sigma} (\vect y - \vect y(\vect x))  \\\label{eqn:core-identify}
  \lim_{\sigma \rightarrow 0}
  \int
  \dd \vect x\,
  \Delta \mt_\tau f(\vect x, t) \,
  K_{\sigma, \vect y} (\vect x)
  % \\\nonumber
  % &=
  % \lim_{\sigma \rightarrow 0}
  % \int
  % \dd \vect x\,
  % f_0(\vect x) \,
  % [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y} (\vect x)\\
  % &=
  % \lim_{\sigma \rightarrow 0}\,
  % \langle
  % [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y}
  % \rangle_0
For convenience, we denote $f_t(\vect x) = f(\vect x, t)$.
Notice that $\mt_\tau f_t(\vect x) = e^{\tau \fwg_t^{2\beta}} f_t(\vect x)$
is the solution of
  \frac{\partial}{\partial \tau} f_t(\vect x, \tau)
  \fwg^{2\beta}(t)  f_t(\vect x, \tau)
  =0
with inital condition $f_t(\vect x, \tau = 0) = f_t(\vect x)$. We do the same
expansion as before, and then
matching different orders of $\varepsilon$ gives:
  &\bigg[
  \frac{\partial}{\partial \tau}
  - \fwg_0^{2\beta}
  f_{t,0}(\vect x, \tau)
  = 0 \\
  &\bigg[
  \frac{\partial}{\partial \tau}
  - \fwg_0^{2\beta}
  f_{t,1}(\vect x, \tau)
  \fwg_1(t) f_{t,0}(\vect x, \tau)
Formally solving these equations with
inital conditions $f_{t,0}(\vect x, 0) = f_t(\vect x) = f(\vect x, t)$
and  $f_{t,1}(\vect x, 0) = 0$ 
\begin{align}\label{eqn:f0-1}
  f_{t,0}(\vect x, \tau)
  e^{\tau\fwg^{2\beta}_0}f_{t,0}(\vect x, 0) \\\label{eqn:f1-1}
  f_{t,1}(\vect x, \tau)
  \int_0^\tau\dd \eta\,
  e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
  \fwg_1(t) f_{t,0}(\vect x,\eta)
  \int_0^\tau\dd \eta\,
  e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
  \fwg_1(t)\circ
  e^{\eta\fwg^{2\beta}_0}f_{t,0}(\vect x, 0) 
By inserting the linear order approximated solution~\eqref{eqn:solv-orig-linear}
in to the above equations, we have:
  \mt_\tau f_t(\vect x)=
  f_{t}(\vect x, \tau)
  e^{\tau\fwg^{2\beta}_0} f_{\inv}^\beta(\vect x) -
  e^{\tau\fwg^{2\beta}_0} \circ
  \\\label{eqn:solve-tau-linear}
  &\,+ \varepsilon
  \int_0^\tau\dd \eta\,
  e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
  \fwg_1(t)\circ
  e^{\eta\fwg^{2\beta}_0}f_{\inv}^\beta(\vect x)  + \mo(\varepsilon^2)
By inserting~\eqref{eqn:solv-orig-linear} and~\eqref{eqn:solve-tau-linear}
into~\eqref{eqn:core-identify}, we have, up to the first order
approximation,
  [\proj\circ\Delta\mt_\tau f](\vect y, t)
  \approx
  \lim_{\sigma \rightarrow 0}
  \bigg\{
    &\,
    \big(e^{\tau\fwg_0^{2\beta}}-\mi\big)
    f_{\inv}^\beta(\vect x)\,
    K_{\sigma,\vect y}(\vect x)\\\nonumber
    &
    - \int_0^t\dd s\,
    \int\dd \vect x\,
    \big(e^{\tau\fwg^{2\beta}_0} - \mi\big)\circ
    \big]\, K_{\sigma,\vect y}(\vect x) \\\nonumber
    &
    \varepsilon
    \int_0^\tau\dd \eta
    \int\dd \vect x\,
    e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
    \fwg_1(t)\circ
    e^{\eta\fwg^{2\beta}_0}f_{\inv}^\beta(\vect x)\,K_{\sigma,\vect y}(\vect x)
    \bigg\}     \\\nonumber
  \approx
  \lim_{\sigma \rightarrow 0}
  \bigg\{
  &\,
    \Big\langle
    \mathbb E_{\vect x}[ K_{\sigma,\vect y}(\vect X^{2\beta}_\tau) ]
    - K_{\sigma,\vect y}(\vect x)
    \Big\rangle\\\nonumber
    &
    - \int_0^t\dd s\,
    \Big\langle
    \mathbb E_{\vect x}\big\{
    \mathbb E_{\vect X_{t-s}^\beta}[
    K_{\sigma,\vect y}(\vect X_\tau^{2\beta})
    ]
    K_{\sigma,\vect y}(\vect X_{t-s}^\beta)
    \Big\rangle\\\label{eqn:core-identify-approx-1}
    &
    \varepsilon
    \int_0^\tau\dd \eta
    \int\dd \vect x\,
    e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
    \fwg_1(t)\circ
    e^{\eta\fwg^{2\beta}_0}f_{\inv}^\beta(\vect x)\,K_{\sigma,\vect y}(\vect x)
    \bigg\}     
Unfortunately the last term on the r.h.s. of~\eqref{eqn:core-identify-approx-1}
is not easy to calculate. We will deal with it with
the path integral method introduced later.

\subsection{Path integral}
The path integral is very useful to develop the non-equilibrium version of
linear response theory. 
Comparing with the idea of ensemble, which is a collection of state points
in the configuration space, the path integral consider the ``ensemble'' of
trajectories.
(In the following, the develop of formula are formal. The strict mathematical
theory is still unclear for me.)
First, we take the standard 1-dimensional Wiener process for example.
Consider the time interval $[0,T]$, the probability density of one trajectory
is given by
\begin{align}
  p[W_t] = \frac 1Z e^{-I[W_t]}
\end{align}
where $I$ is the action functional of Wiener process given by
\begin{align}
  I[W_t] = \int_0^T\frac12 \dot{W}_t^2\dd t
\end{align}
the partition function $Z$ is
\begin{align}
  Z = \int  e^{-I[W_t]} \prod_{0\leq t\leq T}\dd W_t
\end{align}
Consider the following two stochastic processes:
\begin{align}\label{eqn:st-orig}
  \dd \vect X_t &= \vect b(\vect X_t, t) \dd t + \bsigma(\vect X_t, t)\,\dd\vect W_t \\\label{eqn:st-pert}
  \dd \vect Y_t &= \vect b(\vect Y_t, t) \dd t + \vect c(\vect Y_t, t) \dd t + \bsigma(\vect Y_t, t)\,\dd\vect W_t
\end{align}
Where $\vect W_t$ is the standard Wiener process. Obviously
\eqref{eqn:st-pert} is the perturbed version of
\eqref{eqn:st-orig}. It has been shown that, starting from the same
measure saying $\mu$ (which is not necessarily equilibrium or
stationary), the ratio of trajectory probability density between the perturbed
and unperturbed process is~\cite{li2010lecture} (\recheck{I think here
  the incompressibility of phase space should be assumed. Otherwise the
  ratio should be more complicated.})
\begin{align}\label{eqn:girsanov}
  \frac{\dd\mathcal P_{\vect Y}}{\dd\mathcal P_{\vect X}}
  =
  \exp
  \Big\{
  -\frac12 \int_0^T\vert\bsigma^{-1}\cdot\vect c(\vect X_t,t)\vert^2\,\dd t
  +\int_0^T[\dot{\vect X}_t - \vect b(\vect X_t,t)]^T
  \cdot\bsigma^{-T}\cdot\bsigma^{-1}\cdot\vect c(\vect X_t,t)\,\dd t 
  \Big\}
\end{align}
where $\mathcal P_{\vect Y}$ and $\mathcal P_{\vect Y}$ are measures
of the trajectories generated by \eqref{eqn:st-pert} and
\eqref{eqn:st-orig}, respectively.  This result (Girsanov formula?) is
(formally) precise without any approximation.

To be more general, we study the two perturbed Langevin dynamics
(i.e. Eqn.~\eqref{eqn:langevin-1} and \eqref{eqn:langevin-2}) with
different perturbations that are given by $F_e^1(t)$ and $F_e^2(t)$,
respectively. 
By writing Eqn.~\eqref{eqn:langevin-1} and \eqref{eqn:langevin-2} as
\begin{align}
  \left[
    \begin{array}{l}
      \dd\vect q\\
      \dd\vect p
    \end{array}
  \right]
  =
  \left[
    \begin{array}{l}
      \nabla_{\vect p}\mh\\
      -\nabla_{\vect q}\mh - \gamma\vect p + F_e\vect D
    \end{array}
  \right]
  \dd t
  +
  \left[
    \begin{array}{cc}
      \epsilon \vect I & 0\\
      0 & \sigma\vect I
    \end{array}
  \right]
  \cdot
  \left[
    \begin{array}{l}
      \dd\vect W_t\\
      \dd\vect W_t
    \end{array}
  \right]
\end{align}
Using Girsanov's formula, to the leading order of $\Delta F_e = F_e^2 - F_e^1$,
we have
\begin{align}\label{eqn:girsanov-1}
  \frac{\dd\mathcal P^2[\vect X_t]}{\dd\mathcal P^1[\vect X_t]}
  &=
  \exp
  \Big\{
  \frac 1 {\sigma^2}
  \int_0^t
  [\dot{\vect p}_s +
  \gamma\vect p_s +
  \nabla_{\vect q}\mh(\vect q_s,\vect p_s)
  - F_e^1(s) \vect D(\vect q_s,\vect p_s)
  ]\cdot
  \vect D(\vect q_s,\vect p_s)
  \Delta F_e(s)\,
  \dd s
  + \mathcal O(\Delta F_e^2)
  \Big\} 
\end{align}

\subsection{The linear response theory for the core set identification,
  revisited by the path integral}
For some observable $O[\vect X_\eta]$, which is a functional of the
stochastic process $\vect X_\eta$,
the trajectory ensemble average yields:
  \mo(t)
  \int \dd \mu_t(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_t[\vect X_\eta],
where $\mu_t(\vect x)$
is the measure of the initial position, and obviously, we have
$\dd \mu_t(\vect x) = f_t(\vect x)\,\dd \vect x$.
The trajectory $\vect X_\eta \in {\mc\{\vect x,0;\tau\}}$, where
${\mc\{\vect x,0;\tau\}}$ denotes the set of all continuous but not
differentiable trajectories starting at $\vect x$ at artificial
time 0, and ending
at artificial time $\tau$.
$\mathcal P^{2\beta}_t$ denotes the measure of trajectories
developped under temperature $1/2\beta$
at real time $t$.
Since the perturbation is a function of time, this
measure also depends on time. The reference artificial dynamics is chosen
at $t=0$.
In this case, \eqref{eqn:girsanov-1} rewrites:
  \frac{\dd \mathcal P^{2\beta}_t[\vect X_\eta]}
  {\dd \mathcal P^{2\beta}_0[\vect X_\eta]}\,
  \Big\{
  \frac 1 {\sigma^2}
  \int_0^\tau
  [\dot{\vect p}_\eta +
  \gamma\vect p_\eta +
  \nabla_{\vect q}\mh(\vect q_\eta,\vect p_\eta)
  ]\cdot
  \vect D(\vect q_\eta,\vect p_\eta)
  F_e(t)\,
  \dd \eta
  + \mathcal O(\varepsilon^2)
  \Big\}\\
  1+
  F_e(t)\,
  \frac 1 {\sigma^2}
  \int_0^\tau
  [\dot{\vect p}_\eta +
  \gamma\vect p_\eta +
  \nabla_{\vect q}\mh(\vect q_\eta,\vect p_\eta)
  ]\cdot
  \vect D(\vect q_\eta,\vect p_\eta)\,
  \dd \eta
  + \mathcal O(\varepsilon^2)  
Notice that $F_e(t)\sim \mo(\varepsilon)$.
For convenience, we denote
  G[\vect X_\eta] &=
    \frac 1 {\sigma^2}
  \int_0^\tau
  [\dot{\vect p}_\eta +
  \gamma\vect p_\eta +
  \nabla_{\vect q}\mh(\vect q_\eta,\vect p_\eta)
  ]\cdot
  \vect D(\vect q_\eta,\vect p_\eta)\,
  \dd \eta =
  \frac1\sigma\int_0^\tau
  \vect D(\vect q_\eta,\vect p_\eta)
  \cdot\dd \vect W_\eta
where $\vect W_\eta$ is the Wiener process that generates
$\vect X_\eta$.
  \mo(t)
  \int \dd \vect x
  f(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \frac{\dd \mathcal P^{2\beta}_t[\vect X_\eta]}
  {\dd \mathcal P^{2\beta}_0[\vect X_\eta]}\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]  \\\nonumber
  \int \dd \vect x
  f_{0}(\vect x, t)
  + \varepsilon f_{1}(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  1 
  + F_e(t) G[\vect X_\eta]
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \int \dd \vect x
  f_{0}(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \varepsilon
  f_{1}(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]\\\label{eqn:solve-tau-linear-2-0}
  &+
  F_e(t)
  f_{0}(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  G[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
In the case of core set identification,
  [\proj\circ \mt_\tau] f(\vect y,t)
  \int\dd \vect x\,
  \mt_\tau f(\vect x,t) K_{\sigma,\vect y}(\vect x)\\\nonumber
  \int\dd \vect x\,
  e^{\tau\fwg_t^{2\beta}} f(\vect x,t) \,K_{\sigma,\vect y}(\vect x)\\\nonumber
  \int\dd \vect x\,
  f(\vect x,t) \,e^{\tau\bwg_t^{2\beta}}K_{\sigma,\vect y}(\vect x)  \\\nonumber
  \int\dd \vect x\,
  f(\vect x,t) \,\mathbb E_{\vect x}
  K_{\sigma,\vect y}(\vect X^{2\beta}_{t,\tau})
  \\
  \int\dd \vect x\,
  f(\vect x,t) 
  \int_{\mc\{\vect x,0;\tau\}} K_{\sigma,\vect y}(\vect X_\tau)\,
  \dd\mathcal P^{2\beta}_t[\vect X_\eta]
So the observable $O[\vect X_\eta]$
is:
  O[\vect X_\eta] = 
  K_{\sigma,\vect y}(\vect X_\tau),
  % -
  % K_{\sigma,\vect y}(\vect x)
which is the end point of the artificial
trajectory measured by $K_{\sigma,\vect y}$.
Inserting everything we known in~\eqref{eqn:solve-tau-linear-2-0},
and notice $G[\vect X_\eta] = 0$ when $\tau = 0$,
  [\proj\circ\Delta\mt_\tau f](\vect y, t)
  \lim_{\sigma \rightarrow 0}
  \big\{
  &\,
  [\proj\circ\mt_\tau f - \proj\circ\mt_0 f](\vect y, t)
  \big\}\\\nonumber
  \approx
  \lim_{\sigma \rightarrow 0}
  \bigg\{
  &\,
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  [K_{\sigma,\vect y}(\vect X_\tau)
  -K_{\sigma,\vect y}(\vect x)]  \,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]\\\nonumber
  &\,-
  \int_0^t\dd s\, F_e(s)
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  [K_{\sigma,\vect y}(\vect X_\tau)
  -K_{\sigma,\vect y}(\vect x)]  \,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]\\\nonumber
  &\,+
  F_e(t)
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  K_{\sigma,\vect y}(\vect X_\tau)
  % \Big\{
  % \int_0^\tau\dd \eta\,
  % [\dot{\vect p}_\eta + \gamma\vect p_\eta + \nabla_{\vect q}\mh(\vect X_\eta)]
  % \cdot\vect D(\vect X_\eta)
  % \Big\}\,
  \,G[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \bigg\}\\\nonumber
  \approx
  \lim_{\sigma \rightarrow 0}
  \bigg\{
  &\,
  \Big\langle
  \mathbb E_{\vect x}[K_{\sigma,\vect y}(\vect X_\tau^{2\beta})]
  K_{\sigma,\vect y}(\vect x)
  \Big\rangle\\\nonumber
  &\,
  \int_0^t\dd s\, F_e(s)
  \Big\langle
  \mathbb E_{\vect x} \big\{
  \mathbb E_{\vect X^\beta_{t-s}}\big[
  K_{\sigma, \vect y}(\vect X^{2\beta}_\tau)
  K_{\sigma, y}(\vect X^\beta_{t-s})
  \Big\rangle\\\label{eqn:core-identify-approx-2}
  &\,+
  F_e(t)
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  K_{\sigma,\vect y}(\vect X_\tau)
  \,G[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \bigg\}
Comparing~\eqref{eqn:core-identify-approx-2}
with~\eqref{eqn:core-identify-approx-1}, the first
two terms on the r.h.s. are identical. 
The last term is now computable.

\subsection{Higher orders response theory for core set identification}

Here, we assume that the system undergoes a series of perturbations,
which are denoted by $F^0_e(t),\ F^1_e(t),\ \cdots,\ F^i_e(t),\ \cdots$.
Here, $F^0_e(t) = 0$.
The measure for the trajectory space
$\mc\{\vect x, 0; t\}$
is given by
$\mathcal P_0^\beta[\vect X_s],\ \mathcal P_1^\beta[\vect X_s],\ \cdots,\
\mathcal P_i^\beta[\vect X_s], \cdots$, respectively.
The measure for the quenching trajectory are denoted by
$\mathcal P_{0,t}^{2\beta}[\vect X_\eta],\
\mathcal P_{1,t}^{2\beta}[\vect X_\eta],\ \cdots,\
\mathcal P_{i,t}^{2\beta}[\vect X_\eta], \cdots$, respectively.
The notation $t$ on the subscript means the trajectory is branched from
the main trajectory at time $t$.
Now the phase space distribution $f_i(\vect x, t)$ for the
$i$-th perturbation can be studied in terms
of path integral:
  f_i(\vect x, t) =
  \int\dd\vect u\,
  f_i(\vect u, 0)
  \int_{\mc\{\vect u,0; \vect x,t\}}
  \dd\mathcal P_i^\beta[\vect X_s]
Applied by operator $\mt_\tau$, we have
  \mt_\tau f_i(\vect x, t)
  \int\dd\vect u f_i(\vect u, t)
  \int_{\mc\{\vect u,0; \vect x,\tau\}}
  \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]\\
  \int\dd\vect v\,
  f_i(\vect v, 0)
  \int\dd\vect u
  \int_{\mc\{\vect v,0; \vect u,t\}}
  \dd\mathcal P_i^\beta[\vect X_s]  
  \int_{\mc\{\vect u,0; \vect x,\tau\}}
  \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]
For the core set identification,
  [\proj\circ\mt_\tau f](\vect y, t)
  \int\dd\vect v\,
  f_i(\vect v, 0)
  \int\dd\vect u
  \int_{\mc\{\vect v,0; \vect u,t\}}
  \dd\mathcal P_i^\beta[\vect X_s]  
  \int_{\mc\{\vect u,0; \tau\}}
  K_{\sigma,\vect y}(\vect X_\tau)\,
  \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]  \\
  [\proj\circ\mt_0 f](\vect y, t)
  \int\dd\vect v\,
  f_i(\vect v, 0)
  \int_{\mc\{\vect v,0; t\}}
  K_{\sigma,\vect y}(\vect X_t)\,
  \dd\mathcal P_i^\beta[\vect X_s]  
  % \int_{\mc\{\vect u,0; \tau\}}
  % K_{\sigma,\vect y}(\vect X_\tau)\,
  % \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]  
Here we assume that the system always starts from invariant measure,
i.e. $f_i(\vect x, 0) = f_{\inv}^\beta(\vect x)$, and that we have a
good sampling of the $(i-1)$-th perturbation, then
\begin{align}\label{eqn:pert-exact-1}
  [\proj\circ\mt_\tau f](\vect y, t)
  \int\dd\vect v\,
  f_\inv^\beta(\vect v)
  \int\dd\vect u
  \int_{\mc\{\vect v,0; \vect u,t\}}
  \dd\mathcal P_{i-1}^\beta[\vect X_s]  
  \int_{\mc\{\vect u,0; \tau\}}
  \dd\mathcal P_{i-1,t}^{2\beta}[\vect X_\eta]\cdot
  K_{\sigma,\vect y}(\vect X_\tau)\,
  {\dd\mathcal P_{i}^\beta[\vect X_s]}
  {\dd\mathcal P_{i-1}^\beta[\vect X_s]}
  {\dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]}
  {\dd\mathcal P_{i-1,t}^{2\beta}[\vect X_\eta]}
  \\\label{eqn:pert-exact-2}
  [\proj\circ\mt_0 f](\vect y, t)
  \int\dd\vect v\,
  f_{\inv}^\beta(\vect v)
  \int_{\mc\{\vect v,0; t\}}
  \dd\mathcal P_{i-1}^\beta[\vect X_s]
  \cdot
  K_{\sigma,\vect y}(\vect X_t)\,
  {\dd\mathcal P_{i}^\beta[\vect X_s]}
  {\dd\mathcal P_{i-1}^\beta[\vect X_s]}  
  % \int_{\mc\{\vect u,0; \tau\}}
  % K_{\sigma,\vect y}(\vect X_\tau)\,
  % \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]  
Here
\begin{align}\label{eqn:exact-ratio-1}
  {\dd\mathcal P_{i}^\beta[\vect X_s]}
  {\dd\mathcal P_{i-1}^\beta[\vect X_s]}  
  \bigg\{
  \frac{1}\sigma\int_0^t
  \Delta F_e^{i-1}(s)\,\vect D(\vect q_s,\vect p_s)\cdot\dd\vect W_s
  [\Delta F_e^{i-1}(s)]^2\,\vect D^2(\vect q_s,\vect p_s)\,\dd s
  \bigg\}\\\label{eqn:exact-ratio-2}
  {\dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]}
  {\dd\mathcal P_{i-1,t}^{2\beta}[\vect X_\eta]}
  \bigg\{
  \frac{1}\sigma\int_0^\tau
  \Delta F_e^{i-1}(t)\,\vect D(\vect q_\eta,\vect p_\eta)\cdot\dd\vect W_\eta
  \frac 1{2\sigma^2}\int_0^\tau
  [\Delta F_e^{i-1}(t)]^2\,\vect D^2(\vect q_\eta,\vect p_\eta)\,\dd \eta
  \bigg\}
where $\Delta F_e^{i-1}(t) = F_e^{i}(t) - F_e^{i-1}(t) $.
If the trajectory at perturbation $ F_e^{i-1}(t) $ is well sampled, then
\eqref{eqn:exact-ratio-1} and \eqref{eqn:exact-ratio-2} can be measured
without linear approximation.
This is the exact result, from where we can develop
the response (also non-linear) theroy.
Before doing so, we should assume the perturbation can be expanded,
and well approximated in a finite dimensional space:
  F^i_e(t)
  \sum_{j = 1}^\infty
  s^i_j M_j(t)
with this expansion, we have

>>>>

\section{Theoretical background}
\subsection{Classical linear response theory}

In this section, we want to firstly give a brief description of the classical linear response

@@

example.
In this paper we want to study the non-equilibrium system driven by some external force.
More strictly, we investigate the system that is governed by the
following Langevin equation:

@@

  \dot{\vect q} & = \nabla_{\vect p}\mh(\vect q,\vect p), \\\label{eqn:langevin-2}

@@

  + \sigma\dot{\vect W}.

@@

Here $\vect D$ is the external driving force applied to the system, and
$F_e(t)$ is the strength of the driving as a function of time.
We always assume that the magnitude of $\vect D$ is controllable, and
the magnitude of $F_e(t)$ is small and of order $\mo (\varepsilon)$, $\varepsilon \ll 1$.

@@

  \nabla_{\vect p}\cdot\vect D = 0

@@

The equilibrium and non-equilibrium system

@@

vanishing driving force $F_e(t) = 0$ in

@@

We assume that the driving to the

@@

distribution and the un-driven generator
($\vect D = 0$),

@@

which is the un-driven equation. Matching the first and the second order gives:

@@

initial conditions $f_1(\vect x, 0) = 0$ and $f_2(\vect x, 0) = 0$

@@

Where $\bwg^\beta_0$ is the infiniesimal generator of the \emph{un-driven} 

@@

where $\vect X^\beta_t$ is the trajectory of the un-driven Langevin equation

@@

\subsection{The non-equilibrium response theory}

The classical response theory mainly has the following two limitations:
Firstly, one has to start from an equilibrium simulation. That means if the
external driving is no longer small ($\varepsilon$ is relatively big), the
first order (or linear) response~\eqref{eqn:lr} may not be a good approximation to
the true non-equilibrium process any more.
One possible way to improve the accuracy is to introduce the second
order response term, i.e.~\eqref{eqn:f2-0}.
Here one encounters the second limitation of the classical
response theory: it does not provide a frame work, under which
the second and even higher order responses can be easily derived.
The limitations of the classical responses theory motivate us to
develop a more general frame work that allows one starting from any
non-equilibrium process (arbitrarily driven), and calculating from it as many orders of
responses as necessary.

In the language of path integral, the time-dependent average $O( t)$
can be written as

@@

  O( t) =
  \langle O[\vect X_s]\,\rangle_{0,t} = 
  \int\dd \vect u\, f(\vect u, 0) 
  \int_{\mc\{\vect u,0; t\}}
  O[\vect X_s]\, \dd\mathcal P[\vect X_s]  
where $O[\vect X_s]$ is the observable of the trajectories, which is a generalization of the
observable that only depends on the configuration of the system.
$\langle \cdot \,\rangle_{0,t}$ is the ensemble average over all possible trajectories in time interval $[0,t]$.
$f(\vect x, 0)$ is the initial distribution that may not be the equilibrium distribution.
$\mc\{\vect u,0; t\}$ is the set of all continuous trajectories starting from point
$\vect u$ at time $0$, and ending at some position at time $t$.
$\mathcal P[\vect X_s]$ is the
probability measure of the trajectories generated by driven Langevin dynamics~\eqref{eqn:langevin-1}--\eqref{eqn:langevin-2},
where the intensity $F_e$ need not to be 0.
Now we want to consider a system that is a small perturbation of the previous system (we now call it ``reference system'')
in the sense that it has a similar driven force: $F_e + \Delta F_e$, where $\Delta F_e\sim \mo(\varepsilon)$ is small.
The probability measure of the trajectories of this perturbed system is denoted by
$\tilde{\mathcal P}[\vect X_s]$.
The time-dependent average of observable of the system $F_e + \Delta F_e$ can be written down in terms of
the probability measure of the reference system:
  \tilde O(t) =
  \int \dd\vect u f(\vect x,0)
  \int_{\mc\{\vect u,0; t\}} O[\vect X_s]\,
  \frac{\dd\tilde{\mathcal P}[\vect X_s]}{\dd\mathcal P[\vect X_s]}
  \, \dd\mathcal P[\vect X_s]    
by using the Girsanov formula, 
\begin{align}\label{eqn:girsanov}
  {\dd\tilde{\mathcal P}[\vect X_s]}
  {\dd\mathcal P[\vect X_s]}  
  \big\{{G[\vect X_s] - \frac12 H[\vect X_s]}

@@

where the short notations are defined by:

@@

  G[\vect X_s]
  &= \frac{1}\sigma\int_0^t
  \Delta F_e(s)\,\vect D(\vect q_s,\vect p_s)\cdot\dd\vect W_s \\
  H[\vect X_s]
  \Delta F_e^2(s)\,\vect D^2(\vect q_s,\vect p_s)\,\dd s
If the difference $\Delta F_e(t)$ is of order $\mo (\varepsilon)$, then $G[\vect X_s] \sim \varepsilon$ is
the first order term, and $H[\vect X_s] \sim \varepsilon^2$  is the second order term.
Then with the Taylor expansion of the right-hand-side of Eq.~\eqref{eqn:girsanov}, we have
\begin{align}\label{eqn:neq-response}
  \tilde O(t) -
  O(t)

@@

  \big\langle O[\vect X_s]\cdot G[\vect X_s]\big\rangle_{0,t}
  \frac12 \big\langle O[\vect X_s] \cdot (G^2[\vect X_s] - H[\vect X_s] )\big\rangle_{0,t}
  \mo (\varepsilon^3)

@@

Here are some remarks of the main result Eq.~\eqref{eqn:neq-response}:
\begin{itemize}
\item The first term on the right-hand-side of Eq.~\eqref{eqn:neq-response} is the linear
  response of the reference non-equilibrium process (driven by $F_e$). The second term is the second order
  response. One can easily write down higher orders of response by the Taylor expansion
  of the right-hand-side of Eq.~\eqref{eqn:girsanov}.
\item When the observable $O[\vect X_s]$ only depends on the end point of the trajectory, i.e.
  $O[\vect X_s] = O(\vect X_t)$, then $\big\langle O(\vect X_t)\cdot G[\vect X_s]\big\rangle_{0,t}$
  gives the well-know time correlation form of the linear response.
\item If one wants to calculate a large amount of different perturbations, then apply one by one
  Eq.~\eqref{eqn:neq-response} is not convenient, because one has to calculate the responses
  again when the function form of $\Delta F_e$ is not a linear combination of previously calculated perturbations.
  If it is possible to
  express different $\Delta F_e$ by a group of base functions, then the responses are only need
  to calculated on the bases. Then with a linear conbination of the responses on bases, one can derive
  the responses of the whole group of perturbations. 
\item In the prove, we assume that the reference and the perturbed non-equilibrium processes
  have the same initial distribution (both of them may be different from the equilibrium distribution),
  but this is not a necessary. One can easily
  applies similar perturbation approach to the initial distribution as  to the trajectory ensemble.
  To keep the story simple, we do not develop the theory from this aspect.
\end{itemize}
